---
title: "R Notebook"
output: html_notebook
---

```{r}
# Source: https://github.com/dgrtwo/gganimate
install.packages("cowplot")  # a gganimate dependency
devtools::install_github("dgrtwo/gganimate")
```

```{r}
library(gganimate)
library(gapminder)

p <- ggplot(gapminder, aes(gdpPercap, lifeExp, size = pop, color = continent, frame = year)) +
  geom_point() +
  scale_x_log10()

gganimate(p)
```


```{r}
library(ggplot2)
library(gapminder)
library(gganimate)

theme_set(theme_bw())
g <- ggplot(gapminder, aes(gdpPercap, lifeExp, size=pop, frame=year)) +
  geom_point() +
  geom_smooth(aes(group = year), 
      method="lm",
      show.legend=FALSE) +
  facet_wrap(~continent, scales = "free") +
  scale_x_log10()

gganimate(g, interval=0.2)
```

```{r}
install.packages('devtools')
devtools::install_github('thomasp85/gganimate')
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
